Intrusion Detection with Genetic Algorithms and Fuzzy Logic

### 2013-10-16 paper.tex
Made some small changes in the fuzzy genetic algorithm section and also the genetic algorithm section.

\subsection{Rules}
Rules are represented by IF-THEN statements with the following format:

IF (cond1) AND...AND (condm) THEN class = ci

\mycomment{Write more here and figure out how to format the rule}

@@

Duration is the length of the connection in seconds. src\_bytes is the number of bytes sent from source to destination. num\_failed\_logins is the number of failed login attempts. root\_shell returns 1 if root shell is obtained and 0 otherwise. num\_access\_files is the number of operations on access control files. srv\_count is the number of connections to the same service as the current connection in the past two seconds. serror\_rate is the percentage of connections that have ``SYN" errors.
\mycomment{What are SYN errors?}
 same\_srv\_rate is the percentage of connections to the same service.~\cite{KDD99Features}

@@

One record (either an attack or normal activity) is passed into a rule. Each feature in a record is matched to one block of the rule. The parameters of each block measure the probability of an attack using the trapezoidal fuzzy rule shape. The probabilities of each block are then combined by taking the average of the probabilities and comparing them with a threshold to determine if the record is an attack class or normal class.

\subsection{Algorithm Overview}
The algorithm that is used in~\cite{6496342, 6559603} first randomly generates a rule. Then the rule is improved in the training phase. After that, the rules are used to classify the data into classes in the testing phase. Algorithm~\ref{alg:fuzGenAlg} describes the fuzzy genetic algorithm that is used.

@@

  \FOR{each rule}
    \FOR{each attribute}
      \STATE{prob = fuzzy();}
      \STATE{totalprob = totalprob + prob;}
    \ENDFOR

@@

\begin{algorithm}
\caption{Major steps in detection}
\label{alg:detection}
\begin{algorithmic}
\STATE{Initialize the population}
\STATE{crossoverRate = 0.15, mutationRate = 0.35}
\WHILE{number of generation is not reached}
  \FOR{each chromosome in the population}
    \FOR{each precalculated chromosome}
      \STATE{Find fitness}
    \ENDFOR
    \STATE{Assign optimal fitness as the fitness of that chromosome}
  \ENDFOR
  \STATE{Remove some chromosomes with worse fitness}
  \STATE{Apply crossover to the selected pair of chromosomes of the population}
  \STATE{Apply mutation to each chromosome of the population}
\ENDWHILE
\end{algorithmic}
\end{algorithm}

The authors of~\cite{DBLP:journals/corr/abs-1204-1336} used the KDD99 data set. For the training data set, the KDD99 10\% version file was used, and for the testing data set, the KDD99 corrected version file was used.

>>>>

\subsection{Rules}
Rules are represented by IF-THEN statements in the following format:

If <condition> then <action>

\mycomment{Write more here}

@@

Duration is the length of the connection in seconds.

src\_bytes is the number of bytes sent from source to destination. num\_failed\_logins is the number of failed login attempts. root\_shell returns 1 if root shell is obtained and 0 otherwise. num\_access\_files is the number of operations on access control files. srv\_count is the number of connections to the same service as the current connection in the past two seconds. serror\_rate is the percentage of connections that have ``SYN" errors.
\mycomment{What are SYN errors?}
 same\_srv\_rate is the percentage of connections to the same service.~\cite{KDD99Features}

@@

\subsection{Algorithm Overview}
The algorithm that is used in~\cite{6496342, 6559603} first randomly generates a rule. Then the rule is improved in the training phase. After that, the rules are used to classify the data into classes in the testing phase. Algorithm~\ref{alg:fuzGenAlg} describes the fuzzy genetic algorithm that is used. One record (either an attack or normal activity) is passed into a rule. Each feature in a record is matched to one block of the rule. The parameters of each block measure the probability of an attack using the trapezoidal fuzzy rule shape. The probabilities of each block are then combined by taking the average of the probabilities and comparing them with a threshold to determine if the record is an attack class or normal class.

@@

  \FOR{each rule}
    \FOR{each feature}
      \STATE{prob = fuzzy();}
      \STATE{totalprob = totalprob + prob;}
    \ENDFOR

@@

\begin{algorithm}
\caption{Major steps in detection}
\label{alg:detection}
\begin{algorithmic}
\STATE{Initialize the population}
\STATE{crossoverRate = 0.15, mutationRate = 0.35}
\WHILE{number of generation is not reached}
  \FOR{each chromosome in the population}
    \FOR{each precalculated chromosome}
      \STATE{Find fitness}
    \ENDFOR
    \STATE{Assign optimal fitness as the fitness of that

    chromosome}
  \ENDFOR
  \STATE{Remove some chromosomes with worse fitness}
  \STATE{Apply crossover to the selected pair of chromosomes of the population}
  \STATE{Apply mutation to each chromosome of the population}
\ENDWHILE
\end{algorithmic}
\end{algorithm}

\subsection{Experimental Design and Results}
The authors of~\cite{DBLP:journals/corr/abs-1204-1336} used the KDD99 data set. For the training data set, the KDD99 10\% version file was used, and for the testing data set, the KDD99 corrected version file was used. 
\mycomment{Write more here}
